Dialect: A Compact Line Notation Based on SMILES

### 2022-06-20 manuscript.tex
Adds Elements figure. Closes #118

The attributes \ttt{element} (\enquote{element}) and \ttt{isotope} (\enquote{isotope}) define atomic number and neutron count, respectively. Elements are selected from a subset of those approved by IUPAC \cite{periodicTable} (Figure~\ref{fig:elements}). An atom whose element is unknown must have an \ttt{element} attribute equal to \ttt{None}. The \ttt{isotope} attribute is an optional integer value representing an atom's nuclear mass number, defined as the sum of proton and neutron count. Setting the \ttt{isotope} property to \ttt{None} means that the element's isotopic composition equals natural abundance. Otherwise, the lower bound of the value of \ttt{isotope} is one. This lower limit allows for physically nonsensical states such as atoms of negative implied neutron count (e.g., carbon-5). Implementations may reject such atomic states as invalid.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Elements. The element that may be associated with an atom.}
    \label{fig:elements}
\end{figure}

>>>>

The attributes \ttt{element} (\enquote{element}) and \ttt{isotope} (\enquote{isotope}) define atomic number and neutron count, respectively. Elements are selected from a subset of those approved by IUPAC \cite{periodicTable} (Figure~\ref{fig:periodic-table}). An atom whose element is unknown must have an \ttt{element} attribute equal to \ttt{None}. The \ttt{isotope} attribute is an optional integer value representing an atom's nuclear mass number, defined as the sum of proton and neutron count. Setting the \ttt{isotope} property to \ttt{None} means that the element's isotopic composition equals natural abundance. Otherwise, the lower bound of the value of \ttt{isotope} is one. This lower limit allows for physically nonsensical states such as atoms of negative implied neutron count (e.g., carbon-5). Implementations may reject such atomic states as invalid.

\begin{figure}
    \centering
    \includegraphics[width=4in]{periodic-table.pdf}
    \caption{Elements. Available chemical elements and their allowed roles. Not all IUPAC-approved elements are available. Hydrogen counts of atoms associated with elements on blue background can be computed algorithmically. Atoms associated with elements on green background can be selected.}
    \label{fig:periodic-table}
\end{figure}
